Decentralised location proof system

### 2016-04-18 thesis/evaluation.tex
updating after (another) proofread

\section{OTIT conformance}
As explained in section \ref{ssec:otit}, the OTIT model \cite{otit} defines 8 desirable properties of a lcoation proof system. The model introduced in chapter \ref{ch:design} is evaluated with respect to OTIT below.

@@

This property is not enforced at the time of transaction publication in this system. This is to avoid revealing any transaction information to the miner nodes, therefore preserving the privacy of the transaction owner. Instead, the Chronological property is enforced at the time of verification. The chronological link created by adding $KL_{AT}(ID_{A}[n-1]|ts_A)$ to the published transaction will allow Verifier nodes to prove that the transaction is chronologically ordered. Therefore the system preserves OTIT's ``Chronological'' property.

\subsection{Order preserving}
This property states that the order in which location proofs were entered into the proof chain should be maintained.

@@

\subsection{Verifiable}
This states that a Verifier should be able to verify or reject the claim by the user that he has visited the given location(s).

The sytem described in chapter \ref{ch:design} inherently satisfies this property of OTIT. Verifier nodes may be operated by banks, employers, or other parties who have a vested interest in allowing their customers or employees to be able to prove their location. These Verifiers can verify or reject a mobile nodes claimed location by examining the nodes chronological link of transactions (as shown in figure \ref{fig:tree}). The Verifier will revursively generate and examine this tree until it can conclude whether the transaction chain is valid or not.

\subsection{Tamper evident}
The system is tamper evident, meaning the Verifier is able to detect if the proof chain has been tampered with or modified. If a malicious node creates a successful transaction with an honest node, but modifies the transaction data before publishing, a Verifier node will reject the malicious transaction. This rejection will be on the grounds that the matching transaction, published by the honest node, contains contradictory data.

The design assumes the underlying security of the blockchain, so any malicious miner nodes will not be able to tamper with existing transaction data providing that the majority of CPU power in the mining system is owned by honest miners \cite{bitcoin}. Therefore the tamper evident property is satisfied.

@@

In the system, privacy is preserved using \textit{Key Lists} \ref{ssec:key_lists}. Two keys are used for each transaction; $KL_{AT}[n]$ is used to encrypt the \textit{transaction data} for $A$'s $nth$ transaction, and $KL_{AL}[n]$ is used to encrypt the \textit{backwards chronological link} between $A$'s $nth$ transaction and transaction $n-1$.

To control his privacy, a user can choose only to reveal $KL_{AL}[n]$ for a specific transaction $n$. This may be useful if a user does not wish to reveal transaction data for transactions created within a certain distance of his house, for example. Hiding $KL_{AT}[n]$ while revealing $KL_{AL}[n]$ has the advantage of preserving the user's privacy while maintaining a clear backwards chronological link of transactions for the Verifier to follow. This simulatneously preserves both privacy and chronological integrity.

@@

A \textit{sub-set} of size $m$ of a node $A$'s proof chain, beginning at proof $n$, contains all proofs in the sequence $ID_{A}[n-m] - ID_{A}[n]$. Every transaction in this chain is split into two parts (a transaction data and link data part), and separately encrypted. If a node reveals keys for a verifier decrypt all transactions in the sequence $ID_{A}[n-m] - ID_{A}[n]$, it will not be possible for the verifier to discover transaction $ID_{A}[n-m-1]$, or any transaction outside the sequence $ID_{A}[n-m] - ID_{A}[n]$.

@@

In this system, any dishonest user attempting to obtain a location proof with an honest alibi will not succeed, as the honest alibi will abort the exchange (see section \ref{ssec:aborting_exchanges}). A dishonest user who publishes a transaction onto the blockchain with a fabricated alibi will also not succeed, as the transaction will be rejected during verification if a Verifier can't find the matching alibi transaction. The system is therefore not vulnerable to a false presence attack.

\subsection{Malicious intruders}
A malicious intruder offers to help another user to prove a false location, but doesn't prove a false location for himself.

In the context of this system, a malicious intruder may collude with another user to prove a false location, by acting as an alibi. These transactions will be successfully published onto the blockchain. However, if this user attempts to have his transaction chain verified, a Verifier will quickly notice the lack of credible alibis in the proof chain, indicating malicious activity, and reject the proof request. A sample tree of a node with uncredible alibis is shown in figure \ref{fig:uncredible_tree}. This avoids a malicious intruder vulnerability.

\begin{figure}[H]
\begin{center}
\resizebox {0.5\columnwidth} {!} {\input{diagrams/uncredible_tree.tex}}
\vspace{-3cm}
\caption{A proof chain with uncredible alibis}
\label{fig:uncredible_tree}
\end{center}
\end{figure}

@@

Identity discovery is impossible by design in this sytem. By using a different, seemingly random identity for each transaction, it is impossible for a curious user to determine if two transactions belong to the same user or not. It is therefore impossible for a curious user to learn another users identity by monitoring location proofs.

\subsection{Malicious applications}
A malicious application is one that tries to take advantage of a users information as the user seeks verification.

This attack does not affect this system, as a user will only seek verification from applications (verifiers) it deems trustworthy. Verifiers, such as banks or employers, will be known to the user, and therefore trusted. The user also has complete control over which verifiers it chooses to seek verification from, it is not obliged to send verification requests to any verifier.

@@

\subsection{Weak identities}.
In a weak identity attack, a user gives his public key or identity to another colluding user in order to create a location proof.

A weak identity attack will not affect this system. Exchanging public keys or identities between colluding users offers no advantage. This is because the Verifier will ensure that any users requesting verification own the private key corresponding to the public key transferred during the verification request (see section \ref{ssec:verification}).

@@

It is therefore impossible to implicate an honest user in a location proof, without finding vulnerabilities outside the location proof system (for example by compromising their device).

\subsection{False assertion}
In a false assertion attack, two malicious users collude to create false location proofs for themselves.

@@

Providing that the system is comprised of a majority of honest nodes, this attack will not succeed. It will be obvious to a Verifier after construcing a graph of the nodes alibi transaction (as shown in section \ref{ssec:verification}) that the graph lacks alibi credibility, and therefore two malicious users are likely colluding to create location proofs for themselves. Therefore the system is not vulnerable to this attack.

@@

If the proof has not been added to the blockchain yet, then it is possible for the malicous user to modify it to attempt to spoof a false location. However this attack will not work on this system. Any Verifier will reject the transaction on the grounds that it contains contradictory information to the alibis transaction, which has not been modified.

@@

This system is resilient against a most relay attacks. This is because proofs created using a proxy user will be inconsistent with the other proofs in a users proof chain. For example, a user living in New York uses a proxy user to create a proof with a user in London. A Verifier will reject the users claim that it is in London, because of the lack of alibi credibility.

One vulnerability of the system can be called a \textit{complete} relay attack. In a \textit{complete} relay attack, two malicious nodes exist purely for the purpose of proxying location proof. One node, the proxy, will \textit{never} request location proofs for itself. Its only purpose is to proxy exchange data between honest nodes and the other malicious node, the \textit{attacker}.

@@

While some studies have been done on Sybil attacks in decentralised systems \cite{sybil}. There are various methods of mitigating against a subil attack, however a solution for the Sybil attack in a decentralised system is considered an open problem. This system is therefore vulnerable to a highly targeted Sybil attack.

>>>>

\section{OTIT conformance}
As explained in section \ref{ssec:otit}, the OTIT model \cite{otit} defines 8 desirable properties of a location proof system. The model introduced in chapter \ref{ch:design} is evaluated with respect to OTIT below.

@@

This property is not enforced at the time of transaction publication in this system. This is to avoid revealing any transaction information to the miner nodes, therefore preserving the privacy of the transaction owner. Instead, the Chronological property is enforced at the time of verification. The chronological link created by adding $KL_{AT}(ID_{A}[n-1]|ts_A)$ to the published transaction allows Verifier nodes to prove that the transaction is chronologically ordered. Therefore the system preserves OTIT's ``Chronological'' property.

\subsection{Order preserving}
This property states that the order in which location proofs are entered into the proof chain should be maintained.

@@

\subsection{Verifiable}
This states that a Verifier should be able to verify or reject the claim by the user that it has visited the given location(s).

The sytem described in chapter \ref{ch:design} inherently satisfies this property of OTIT. Verifier nodes may be operated by banks, employers, or other parties who have a vested interest in allowing their customers or employees to be able to prove their location. These Verifiers can verify or reject a mobile nodes claimed location by examining the nodes chronological link of transactions (as shown in figure \ref{fig:tree}). The Verifier will recursively generate and examine this tree until it can conclude whether or not the transaction chain is valid.

\subsection{Tamper evident}
The system is tamper evident, meaning that a Verifier is able to detect if the proof chain has been tampered with or modified. If a malicious node creates a successful transaction with an honest node, but modifies the transaction data before publishing, a Verifier node will reject the malicious transaction. This rejection will be on the grounds that the matching transaction, published by the honest node, contains contradictory data.

The design assumes the underlying security of the blockchain, so any malicious miner nodes will not be able to tamper with existing transaction data providing that the majority of CPU power in the miner network is owned by honest miners \cite{bitcoin}. Therefore the tamper evident property is satisfied.

@@

In the system, privacy is preserved using \textit{Key Lists} (See section \ref{ssec:key_lists}). Two keys are used for each transaction; $KL_{AT}[n]$ is used to encrypt the \textit{transaction data} for node $A$'s $nth$ transaction, and $KL_{AL}[n]$ is used to encrypt the \textit{backwards chronological link} between node $A$'s $nth$ transaction and transaction $n-1$.

To control its privacy, a user can choose only to reveal $KL_{AL}[n]$ for a specific transaction $n$. This may be useful if a user does not wish to reveal transaction data for transactions created within a certain distance of its house, for example. Hiding $KL_{AT}[n]$ while revealing $KL_{AL}[n]$ has the advantage of preserving the user's privacy while maintaining a clear backwards chronological link of transactions for a Verifier to follow. This simultaneously preserves both privacy and chronological integrity.

@@

A \textit{sub-set} of size $m$ of a node $A$'s proof chain, beginning at proof $n$, contains all proofs in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$. Every transaction in this chain is split into two parts, a transaction data and link data part, and separately encrypted. If a node reveals keys for a Verifier to decrypt all transactions in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$, it will not be possible for the Verifier to discover transaction $ID_{A}[n-m-1]$, or any transaction outside the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$.

@@

In this system, any dishonest user attempting to obtain a false location proof with an honest alibi will not succeed, as the honest alibi will abort the exchange (see section \ref{ssec:aborting_exchanges}). A dishonest user who publishes a transaction onto the blockchain with a fabricated alibi will also not succeed, as the transaction will be rejected during verification if a Verifier can't find the matching alibi transaction. The system is therefore not vulnerable to a false presence attack.

\subsection{Malicious intruders}
A malicious intruder offers to help another user to prove a false location, but doesn't prove a false location for itself.

In the context of this system, a malicious intruder may collude with another user to prove a false location, by acting as an alibi. These transactions will be successfully published onto the blockchain. However, if this user attempts to have its transaction chain verified, a Verifier will quickly notice the lack of credible alibis in the proof chain, indicating malicious activity, and reject the proof request. A sample tree of a node with uncredible alibis is shown in figure \ref{fig:uncredible_tree}. This avoids a malicious intruder vulnerability.

\begin{figure}[H]
\begin{center}
\resizebox {0.6\columnwidth} {!} {\input{diagrams/uncredible_tree.tex}}
\vspace{-3.25cm}
\caption{A proof chain with uncredible alibis}
\label{fig:uncredible_tree}
\end{center}
\end{figure}

@@

Identity discovery is impossible by design in this system. By using a different, seemingly random identity for each transaction, it is impossible for a curious user to determine if two transactions belong to the same user or not. It is therefore impossible for a curious user to learn another user's identity by monitoring location proofs.

\subsection{Malicious applications}
A malicious application is one that tries to take advantage of a user's information as the user seeks verification.

This attack does not affect this system, as a user will only seek verification from applications (Verifiers) it deems trustworthy. Verifiers, such as banks or employers, will be known to the user, and therefore trusted. The user also has complete control over which Verifiers it chooses to seek verification from, it is not obliged to send verification requests to any Verifier.

@@

\subsection{Weak identities}
In a weak identity attack, a user gives its public key or identity to another colluding user in order to create a location proof.

A weak identity attack will not affect this system. Exchanging public keys or identities between colluding users offers no advantage. This is because a Verifier will ensure that any users requesting verification own the private key corresponding to the public key transferred during the verification request (see section \ref{ssec:verification}).

@@

It is therefore impossible to implicate an honest user in a location proof, without exploiting vulnerabilities outside the location proof system (for example by compromising the underlying assumed security of the device).

\subsection{False assertion}
In a false assertion attack, two malicious users collude to create false location proofs for each other.

@@

Providing that the system is comprised of a majority of honest nodes, this attack will not succeed. It will be obvious to a Verifier after constructing a graph of the node's alibi transaction (as shown in section \ref{ssec:verification}) that the graph lacks alibi credibility, and therefore two malicious users are likely colluding to create location proofs for themselves. Therefore the system is not vulnerable to this attack.

@@

If the proof has not been added to the blockchain yet, then it is possible for the malicious user to modify it to attempt to spoof a false location. However this attack will not work on this system. Any Verifier will reject the transaction on the grounds that it contains contradictory information to the alibis transaction, which has not been modified.

@@

This system is resilient against most relay attacks. This is because proofs created using a proxy user will be inconsistent with the other proofs in a users proof chain. For example, a user living in New York uses a proxy user to create a proof with a user in London. A Verifier will reject the users claim that it is in London, because of the lack of alibi credibility.

One vulnerability of the system can be called a \textit{complete} relay attack. In a \textit{complete} relay attack, two malicious nodes exist purely for the purpose of proxying location proof. One node, the proxy, will \textit{never} request location proofs for itself. Its only purpose is to proxy exchange data between honest nodes and the other malicious node, the \textit{attacker}. The attacker will never request a proof by itself, it will always route its requests through the proxy user.

@@

Previous work has shown that preventing a Sybil attack is impossible in a fully decentralised system \cite{sybil}. This system is therefore vulnerable to a highly targeted Sybil attack. However, there are various possible methods of mitigating against such an attack.

Introducing a penalty for identity creation would mitigate against an attempted large-scale Sybil attack. For example, if a node is required to solve a proof-of-work puzzle before creating an identity, a large-scale Sybil attack would prove extremely computationally expensive for the attacker. This is an impractical mitigation however, as this system is designed to operate on mobile phones. Mobile phones should not be forced to complete proof-of-work puzzles, as computational resources and power supply is very limited when compared with miner nodes, which are servers.

Another possible mitigation involves using a web of trust, which  allows users of a system to express their trust of other users \cite{weboftrust}. Users of the system build a large network of trust relationships, allowing other users to assess the trustworthiness of a potential alibi before creating an exchange with it. This technique of mitigating against the Sybil attack would involve a trade-off with the privacy protecting features currently present in the system, because a web of trust requires globally unique, static user identification to operate. This system uses non-unique, dynamic user identification in order to preserve privacy.

Previous research \cite{sybil} has concluded that the only provably correct way of preventing a Sybil attack in a decentralised system is to use a \textit{centralised} name system to coordinate the distribution of identities. Therefore a Sybil attack vulnerability must be taken out of the scope of this system, as this system is focused on a decentralised approach to location verification.

### 2016-04-18 thesis/introduction.tex
updating after (another) proofread

\section{Project and Motivation}
Location verification is the process of verifying whether a \textit{node} (computer) is physically present at a location it claims to be. Existing location proof systems attept to use centralised, trusted ``authoritive'' nodes to provide proof of another node's location. These approaches require investment in infrastructure, and are subject to privacy violation and denial of service attacks. This project aims to present a \textit{decentralised} solution to this problem. A decentralised location proof system is a system in which there is no ``authoritive source'' trusted and relied upon to provide and store sensitive location information.

This project describes a decentralised location proof system that is capable of operating on \textit{mobile nodes} (mobile devices). I propose a design in which location proofs are obtained using other untrusted mobile nodes as \textit{alibi's}. Proofs will be created as two mobile nodes communicate over an ad-hoc bluetooth network, transfer encrypted location information, and publish it on a public append-only bulletin board, known as a \textit{blockchain}. The decentralised nature of the system means that there is no single point of failure, no entity controlling the security of every node's location proofs, and no entity capable of violating another node's privacy. This is because in a decentralised system, no node is ``in charge'', and no node has more authority in the system than any other node.

\section{Report outline}
This report consists of four additional chapters, listed biefly below.

\subsection{Background}
Chapter 2 begins with a brief introduction to the problem space. A brief explanation of decentralised and distributed networks, as well as the blockchain is then presented, in the context of location proof systems. The chapter closes with an explanation of the design goals defined for this project.

@@

\subsection{Future work}
Chapter 5 presents the conclusions of the project, and details interesting areas for possible future work relating to the project.

>>>>

\section{Project and motivation}
Location verification is the process of verifying whether a \textit{node} (computer) is physically present at a location it claims to be. There are two general categories of location verification; \textit{observation} and \textit{proof}. In location observation, a user's location is determined by observing certain properties of the user, its IP address for example. This is a cheap but very unreliable method of location verification. In location proof, a user's location can be proven reliably.

Existing location proof systems attempt to use centralised, trusted ``authoritative'' nodes to provide proof of another node's location. These approaches require investment in infrastructure, and are subject to privacy violation and denial of service attacks. This project aims to present a \textit{decentralised} solution to this problem. A decentralised location proof system is a system in which there is no ``authoritative source'' trusted and relied upon to provide and store sensitive location information.

This project describes a decentralised location proof system that is capable of operating on \textit{mobile nodes} (mobile devices). I propose a design in which location proofs are obtained using other untrusted mobile nodes as \textit{alibis}. Proofs will be created as two mobile nodes communicate over an ad-hoc bluetooth network, transfer encrypted location information, and publish it on a public append-only bulletin board, known as a \textit{blockchain}. The decentralised nature of the system means that there is no single point of failure, no entity controlling the security of every node's location proofs, and no entity capable of violating another node's privacy. This is because in a decentralised system, no node is ``in charge'', and no node has more authority in the system than any other node.

\section{Report outline}
This report consists of four additional chapters, listed briefly below.

\subsection{Background}
Chapter 2 begins with an introduction to the problem space. A brief explanation of decentralised and distributed networks, as well as the blockchain is then presented, in the context of location proof systems. The chapter closes with an explanation of the design goals defined for this project.

@@

\subsection{Conclusion and Future Work}
Chapter 5 presents the conclusions of the project, and details interesting areas for possible future work relating to the project.

### 2016-04-18 thesis/thesis.tex
Updates after proofreading Introduction and Design chapters
Adding evaluation chapter
updating after (another) proofread

\usepackage{tikz}
\usetikzlibrary{calc,arrows}
\usepackage{enumitem}
\usepackage{float}
\usepackage{subfig}

@@

\begin{document}
\maketitle

@@

\chapter{Introduction}
\input{introduction.tex}

\chapter{Background}
\input{background.tex}

\chapter{Design}
\input{design.tex}

\chapter{Evaluation}
\input{evaluation.tex}

\chapter{Future work}

@@

\bibitem{sybil}
  J.R. Douceur,
  ``The sybil attack'',
  Druschel, P., Kaashoek, M.F., Rowstron, A. (eds.) IPTPS 2002. LNCS, vol. 2429, pp. 251–260,
  Springer, Heidelberg (2002).

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{matrix,positioning,arrows.meta,arrows,calc}
\usepackage{enumitem}
\usepackage{float}
\usepackage{subfig}

@@

\begin{document}
\pagenumbering{roman}
\maketitle

@@

\pagenumbering{arabic}
\chapter{Introduction} \label{ch:introduction}
\input{introduction.tex}

\chapter{Background} \label{ch:background}
\input{background.tex}

\chapter{Design} \label{ch:design}
\input{design.tex}

\chapter{Evaluation} \label{ch:evaluation}
\input{evaluation.tex}

\chapter{Conclusion and Future Work} \label{ch:conclusion}
\input{conclusion.tex}

@@

\bibitem{sybil}
  J. Douceur,
  ``The Sybil Attack'',
  In First IPTPS,
  March 2002.

@@

\bibitem{weboftrust}
  R. V. Guha, R. Kumar, P. Raghavan, and A. Tomkins,
  ``Propagation of trust and distrust'',
  in Proceedings of WWW, pp. 403–412,
  2004.
